# Overview

This project parses Alma Analytics `.catalog` files and extracts metadata from OBIEE reports.

This notebook is designed to be self-contained and reproducible. It does not use interactive prompts such as `file.choose()` or `menu()`. Instead, it uses project-relative paths so the notebook can be rendered consistently by anyone who clones the repository.

The workflow is:

1. Load the helper functions.
2. Read the Alma Analytics catalog file.
3. Locate the analysis script.
4. Run the analysis.
5. Preview the results.
6. Export the results.

## Load packages and helper functions

```{r}
library(here)

source(here(
  "scripts",
  "script_helper_functions",
  "read_catalog_file.R"
))
```

## Read catalog

```{r}
catalog_file <- here(
  "data",
  "Catalog files",
  "FiltersAnnualStatistics2025-26.catalog"
)

if (!file.exists(catalog_file)) {
  stop("Catalog file not found: ", catalog_file)
}

catalog <- read_catalog_file(catalog_file)
```

## Select analysis script

```{r}
analysis_scripts <- list.files(
  here("scripts", "extract_scripts"),
  pattern = "\\.[Rr]$",
  full.names = TRUE
)

if (length(analysis_scripts) == 0) {
  stop("No analysis scripts found in scripts/extract_scripts/")
}

if (length(analysis_scripts) > 1) {
  stop(
    "Multiple analysis scripts found. ",
    "Specify which one to use or keep only one script in scripts/extract_scripts/."
  )
}

analysis_script <- analysis_scripts[1]

cat("Running:", basename(analysis_script), "\n")
```

## Run analysis

```{r}
source(analysis_script)
```

The analysis script should create an object named `results`.

## Preview results

```{r}
if (exists("results")) {
  head(results)
} else {
  stop("The analysis script did not create an object named 'results'.")
}
```

## Export results

```{r}
dir.create(
  here("data", "processed"),
  recursive = TRUE,
  showWarnings = FALSE
)

output_file <- here(
  "data",
  "processed",
  paste0(
    tools::file_path_sans_ext(basename(catalog_file)),
    "_",
    tools::file_path_sans_ext(basename(analysis_script)),
    ".csv"
  )
)

write.csv(results, output_file, row.names = FALSE)

cat("Results written to:\n", output_file, "\n")
```