# Overview

This project parses Alma Analytics `.catalog` files and extracts metadata from OBIEE reports.

For a Quarto notebook, the goal is to make the notebook self-contained and reproducible. You should replace anything that depends on file.choose() with a path that's determined automatically.

The workflow is:

1.  Select a catalog file from `data/Catalog files/`.
2.  Source the helper functions.
3.  Select an analysis script from `scripts/extract_scripts/`.
4.  Run the analysis.
5.  Export the results to `data/processed/`.

## Load helper functions

```{r}
helper_scripts <- list.files(
  "scripts/script_helper_functions",
  pattern = "\\.[Rr]$",
  full.names = TRUE
)

invisible(lapply(helper_scripts, source))

## Select a catalog file

catalog_files <- list.files(
  "data/Catalog files",
  pattern = "\\.catalog$",
  full.names = TRUE,
  recursive = TRUE
)

if (length(catalog_files) == 0) {
  stop("No .catalog files found in data/Catalog files/")
}

selection <- menu(
  basename(catalog_files),
  title = "Choose a catalog file"
)

if (selection == 0) {
  stop("No catalog file selected.")
}

catalog_file <- catalog_files[selection]
catalog_file
```

## Read catalog

```{r}
catalog_file <- "data/Catalog files/Campus Categorization Reports.catalog"
```

## Select an analysis

This `.qmd` file should never ask the user what to do, so for the purposes of this .qmd notebook

```{r}
# analysis_scripts <- list.files(
#   "scripts/extract_scripts",
#   pattern = "\\.[Rr]$",
#   full.names = TRUE
# )
# 
# if (length(analysis_scripts) == 0) {
#   stop("No analysis scripts found in scripts/extract_scripts/")
# }
# 
# selection <- menu(
#   basename(analysis_scripts),
#   title = "Choose an analysis"
# )
# 
# if (selection == 0) {
#   stop("No analysis selected.")
# }
# 
# analysis_script <- analysis_scripts[selection]
# analysis_script
```

## Run analysis

```{r}
source(analysis_script)
```

The selected script should create an object called `results`.

## Preview results

```{r}
if (exists("results")) {
  head(results)
} else {
  cat("No object named 'results' was created by the analysis script.\n")
}
```

## Export results

```{r}
if (exists("results")) {
  dir.create("data/processed", recursive = TRUE, showWarnings = FALSE)

  output_file <- file.path(
    "data/processed",
    paste0(
      tools::file_path_sans_ext(basename(catalog_file)),
      "_",
      tools::file_path_sans_ext(basename(analysis_script)),
      ".csv"
    )
  )

  write.csv(results, output_file, row.names = FALSE)

  cat("Results written to:\n", output_file, "\n")
}
```

```         
```
